Exploring Rural Shrink Smart Through Guided Discovery Dashboards

### 2022-08-01 SDSS Journal Paper/Paper Draft.Rmd
more edits from reread

In our statistical graphs, we used Parallel Coordinate Plots (PCPs) to allow the user to look at a variety of variables, while the Guided Discovery Learning was used to makes sure that the users were informed of the information that was presented, it did not allow for the town leaders any more ease in understanding. This direction will be limited but may be useful for the sake of ease on the town leaders. In the event that we want to continue to have the town leaders explore using a different statistical graphic, we would like to introduce a flower plot. This method may not represent that data in the way that could be misleading for understanding, we believe that the flower plot will allow for town leaders to engage in being curious as they explore more dimensions of data related to their Quality of Life (QoL) survey.

EDA can be a difficult for a variety of groups of people, novice users and experienced researchers. While working with a variety of  disciplines because EDA can be hard to understand the use cases of exploration of data. Many experience researchers, see EDA as a way to look at data that were collected to only describe the behavior of variables that are added into models or research questions. However, EDA can be used in a data discovery, such as the work displayed in this article. Data Discovery can help with the quality of the data, in order to find new resources. EDA can help with potential causality of town related issues. For example, if data are showing that people are no longer using public transportation, this could be due to the population shrinking but exploring the data could suggest that more people are using ride share companies. This could as suggest that public transportation may not offer the needs for the people in the town. EDA will help identify those issues or even allow for the town leaders to look for answers.

\section {Conclusions}

In conclusion, using a less known statistical graphic, our ideas of using Guided Discovery Learning was used to make sure that the users were informed of the information that was presented, it did not allow for the town leaders any more ease in understanding. As a result, we decided to look for easier ways to display data, such as boxplots and barplots. This direction will be limited but may be useful for the sake of ease on the town leaders.

@@

With the lack of research in dashboard design, it could be challenging to develop a dashboard with a clear layout and clear intention. This lack of clarity outside of dashboard pitfalls could lend the dashboard to miss key components that are useful. This is a generalization not only for our research but along all types of dashboard design. We are encouraged to minimize an interface that will not overwhelm the user, but what types of components, which components should be used can be a struggle for our research.

When showing our apps to internal research members, it was difficult to collective incorporate what was wanted and what was needed to empower collaborators to help brainstorm. Once, a design was presented, there were polarizing responses from no feedback to a dramatic change of the app layout. At times, collaborators could feel as if there suggestions were not being heard or dismissed. Along with the intention of the new designs could have been lost in translation due to the lack of being incorporated earlier or more often. As a result both groups become frustrated.

>>>>

Parallel Coordinate Plots (PCPs) allowed the user to look at multidimensional variables, while the Guided Discovery Learning was used to make sure that users were informed of the information that was presented, it did not provide the town leaders any more ease in understanding our statistical graphic. Our new proposed direction will be limited but may be useful for the sake of ease on the town leaders and allow for the exploration into other pieces of data, by using a flower plot method. This method may not represent that data in the way that could be misleading of the whole picture of the town, we believe that the flower plot will allow for town leaders to engage in being curious as they explore more dimensions of data related to their Quality of Life (QoL) survey.

While working with a variety of disciplines, EDA can be a difficult for a variety of groups of people, novice users and experienced researchers. Because EDA can be hard to understand when the idea of EDA is only to prepare for modeling. However, EDA can be used in a data discovery, such as the work displayed in this article. Data Discovery can help with the quality of the data, in order to find new resources.

\section{Conclusions}

In conclusion, using a less known statistical graphic, PCPs, to the novice users was used to make sure that the users were informed of the multidimensional aspect of their information to help data driven decision making. As a result, we decided to look for easier ways to display data, such as boxplots, barplots, or flower plots. This direction will be limited but may be useful for the sake of ease on the town leaders.

@@

With the lack of research in dashboard design, it could be challenging to develop a dashboard with a clear layout and clear intention. This lack of clarity outside of dashboard pitfalls by Stephen Few could lend the dashboard to miss key components that are useful. This is a generalization not only for our research but across all types of dashboard design. We are encouraged to minimize an interface that will not be overwhelming the user, but in what order should these components should be used can be a struggle for our research.

When showing our applications versions to internal research members, it was difficult to collective incorporate necessary components and empower collaborators to help brainstorm. Once a design was presented, there were polarizing responses from no feedback to a dramatic change of the dashboard layout. At times, collaborators could feel as if there suggestions were not being heard or dismissed. Along with the intention of the new designs could have been lost in translation due to the lack of being incorporated earlier or more often. As a result both groups become frustrated. As a result our finalizing motto will be to "test often and test again," this will help ease the feeling of exclusivity with our collaborators.

### 2022-08-01 SDSS Journal Paper/Paper-Draft.tex
more edits from reread

With the lack of research in dashboard design, it could be challenging to develop a dashboard with a clear layout and clear intention. This lack of clarity outside of dashboard pitfalls could lend the dashboard to miss key components that are useful. This is a generalization not only for our research but along all types of dashboard design. We are encouraged to minimize an interface that will not overwhelm the user, but what types of components, which components should be used can be a struggle for our research.

When showing our apps to internal research members, it was difficult to collective incorporate what was wanted and what was needed to empower collaborators to help brainstorm. Once, a design was presented, there were polarizing responses from no feedback to a dramatic change of the app layout. At times, collaborators could feel as if there suggestions were not being heard or dismissed. Along with the intention of the new designs could have been lost in translation due to the lack of being incorporated earlier or more often. As a result both groups become frustrated.

>>>>

With the lack of research in dashboard design, it could be challenging to develop a dashboard with a clear layout and clear intention. This lack of clarity outside of dashboard pitfalls by Stephen Few could lend the dashboard to miss key components that are useful. This is a generalization not only for our research but across all types of dashboard design. We are encouraged to minimize an interface that will not be overwhelming the user, but in what order should these components should be used can be a struggle for our research.

When showing our applications versions to internal research members, it was difficult to collective incorporate necessary components and empower collaborators to help brainstorm. Once a design was presented, there were polarizing responses from no feedback to a dramatic change of the dashboard layout. At times, collaborators could feel as if there suggestions were not being heard or dismissed. Along with the intention of the new designs could have been lost in translation due to the lack of being incorporated earlier or more often. As a result both groups become frustrated. As a result our finalizing motto will be to ``test often and test again,'' this will help ease the feeling of exclusivity with our collaborators.
